MSHS COVID-19 Vaccination Summary

### 2022-09-27 MSHS Vaccines Administered Hybrid Data Model.Rmd
Update analysis reference file. Update code for hybrid dashboard to create new repo each week.

```{r Set directory, import reference data, and repository, include = FALSE}
# Set working directory and select raw data ----------------------------
rm(list = ls())

# Determine path for working directory
if ("Presidents" %in% list.files("J://")) {
  user_directory <- paste0("J:/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
} else {
  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
}

@@

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

```{r Import existing repo and append as needed}
# Import schedule repository daily summary for 2020 and 2021
sched_repo_summary <- readRDS(
  paste0(user_directory,
         "/Hybrid Repo Sched & Admin Data",
         "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

@@

@@

  # Select most recent weekly file
  weekly_vax_admin <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report/*.*"))

  weekly_vax_admin <- read.csv(weekly_vax_admin)

@@

  weekly_vax_admin <- weekly_vax_admin %>%
    select(-DOSE) %>%
    mutate(VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
                            "Peds (Pfizer 5-11yo)",
                            ifelse(str_detect(IMMUNE_NAME,
                                              "(\\(6 MONTHS - 4 YEARS\\))") |
                                     str_detect(IMMUNE_NAME,
                                                "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                                   "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)", 
                                   "Adult (12yo+)")),
           Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
                        ifelse(str_detect(IMMUNE_NAME, "MODERNA") |
                                 str_detect(
                                   IMMUNE_NAME,
                                   "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                               "Moderna",
                               ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
                                      NA))),
           Dose = ifelse(
             str_detect(replace_na(PRC_NAME, ""), "DOSE 1"), "Dose 1",
             ifelse(
               str_detect(replace_na(PRC_NAME, ""), "DOSE 2"), "Dose 2",
               ifelse(
                 str_detect(replace_na(PRC_NAME, ""), "(DOSE 3)|(BOOSTER)"),
                 "Dose 3/Booster",
                 ifelse(
                   str_detect(replace_na(RESPONSE_LIST, ""), "First Dose"),
                   "Dose 1",
                   ifelse(
                     str_detect(replace_na(RESPONSE_LIST, ""), "Second Dose"),
                     "Dose 2",
                     ifelse(
                       str_detect(replace_na(RESPONSE_LIST, ""),
                                  "(Third Dose) | (Booster Dose)"),
                       "Dose 3/Booster",
                       ifelse(VaxType %in% "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)",
                              "Dose 1", "Dose 3/Booster"))))))),
           Date = as.Date(str_extract(IMMUNE_DATE,
                                      "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
                          format = "%d-%b-%Y")
           ) %>%
    rename(Department = DEPARTMENT_NAME)

@@

  # Save new repository
  saveRDS(sched_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

>>>>

```{r Set directory, import reference data, and repository, include = FALSE}
# # Determine path for working directory
# if ("Presidents" %in% list.files("J://")) {
#   user_directory <- paste0("J:/Presidents/HSPI-PM/",
#                            "Operations Analytics and Optimization/Projects/",
#                            "System Operations/COVID Vaccine")
# } else {
#   user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
#                            "Operations Analytics and Optimization/Projects/",
#                            "System Operations/COVID Vaccine")
# }

@@

# Import reference data for site and pod mappings
# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(
  user_directory,
  "/Hybrid Repo Sched & Admin Data",
  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
  sheet = "Hybrid Dept Mapping")

@@

```{r Import existing repo and append as needed}
if (initial_run) {

  # Import schedule repository daily summary for 2020 and 2021
  sched_repo_summary <- readRDS(
    paste0(user_directory,
           "/Hybrid Repo Sched & Admin Data",
           "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
} else {

  # Select repository
  repo_file <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report",
             "/*.*"),
    caption = "Select hybrid vaccine administration repository.")

  hybrid_repo <- readRDS(repo_file)

@@

  # Select most recent weekly file
  weekly_vax_admin <- choose.files(
    default = 
      paste0(user_directory,
             "/Epic Vaccines Administered Report",
             "/Weekly Automated Reports/*.*"),
    caption = "Select weekly vaccine administration data.")

  weekly_vax_admin <- read_excel(weekly_vax_admin)

@@

  weekly_vax_admin <- weekly_vax_admin %>%
    select(-DOSE) %>%
    mutate(VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
                            "Peds (Pfizer 5-11yo)",
                            ifelse(str_detect(IMMUNE_NAME,
                                              "(\\(6 MONTHS - 4 YEARS\\))") |
                                     str_detect(IMMUNE_NAME,
                                                "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                                   "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)", 
                                   "Adult (12yo+)")),
           Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
                        ifelse(str_detect(IMMUNE_NAME, "MODERNA") |
                                 str_detect(
                                   IMMUNE_NAME,
                                   "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
                               "Moderna",
                               ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
                                      NA))),
           Dose = ifelse(
             str_detect(replace_na(PRC_NAME, ""), "DOSE 1"), "Dose 1",
             ifelse(
               str_detect(replace_na(PRC_NAME, ""), "DOSE 2"), "Dose 2",
               ifelse(
                 str_detect(replace_na(PRC_NAME, ""), "(DOSE 3)|(BOOSTER)"),
                 "Dose 3/Booster",
                 ifelse(
                   str_detect(replace_na(RESPONSE_LIST, ""), "First Dose"),
                   "Dose 1",
                   ifelse(
                     str_detect(replace_na(RESPONSE_LIST, ""), "Second Dose"),
                     "Dose 2",
                     ifelse(
                       str_detect(replace_na(RESPONSE_LIST, ""),
                                  "(Third Dose) | (Booster Dose)"),
                       "Dose 3/Booster",
                       ifelse(VaxType %in% "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)",
                              "Dose 1", "Dose 3/Booster"))))))),
           Date = as.Date(IMMUNE_DATE)) %>%
    rename(Department = DEPARTMENT_NAME)

@@

  # Save new repository
  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                             "Hybrid Vaccine Admin Data ",
                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
                             format(max(hybrid_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
